Supporting Information for\\ ``A weakly structured stem for human origins in Africa''

### 2022-09-01 supplement.tex
cleaned up captions v2

\begin{figure}[ht]
    \centering
    \includegraphics{figures/supp-f4s-continuous-migration.pdf}
    \caption{
        \textbf{Predicted \bm{$f_4$} between pairs of contemporary human populations
        and ancient branches from the continuous-migration model.}
        Despite population structure inferred to have extended up to 1Ma
        into the past, differentiation between contemporary African populations
        only traces back to differentiation between ancestral populations
        $\sim$100-200ka, indicating that while stem populations were structured
        (Fig.~\ref{fig:supp-FST-panels}), differentiation due to that
        ancient structure contributes little to differentiation between contemporary
        populations.
    }
    \label{fig:supp-f4s-continuous-migration}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics{figures/supp-f4s-merger-without-stem-migration.pdf}
    \caption{
        \textbf{Predicted \bm{$f_4$} between pairs of contemporary human populations
        and ancient branches from the merger-without-stem-migration model.}
        Unlike the continuous-migration model, population structure in the stems
        following the divergence of Neanderthal and human ancestors results
        in differentiation among contemporary populations that aligns with drift
        between the stems. In this model, migration between stem populations
        is disallowed.
    }
    \label{fig:supp-f4s-merger-without-stem-migration}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics{figures/supp-f4s-merger-with-stem-migration.pdf}
    \caption{
        \textbf{Predicted \bm{$f_4$} between pairs of contemporary populations
        and ancient branches from the merger-with-stem-migration model.}
        Differentiation between present-day populations aligns with
        up to $\approx 5\%$ of the drift between stems, although some
        population pairs show even less shared drift.
    }
    \label{fig:supp-f4s-merger-with-stem-migration}
\end{figure}

>>>>

\begin{figure}[ht]
    \centering
    \includegraphics{figures/supp-f4s-continuous-migration.pdf}
    \caption{
        \textbf{Predicted \bm{$f_4$} between pairs of contemporary human populations
        and ancient branches from the continuous-migration model.} 
        $f_4^2(A, B; X, Y)/f_2(A, B)f_2(X, Y)$ is interpreted as the proportion of the
        amount of drift between sampled populations $A$ and $B$ that aligns with
        drift between populations $X$ and $Y$, sampled in the past
        (see Section~\ref{sec:f4}).
        Despite population structure inferred to have extended up to 1Ma
        into the past, differentiation between contemporary African populations
        only traces back to differentiation between ancestral populations
        $\sim$100-200ka, indicating that while stem populations were structured
        (Fig.~\ref{fig:supp-FST-panels}), differentiation due to that
        ancient structure contributes little to differentiation between contemporary
        populations.
    }
    \label{fig:supp-f4s-continuous-migration}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics{figures/supp-f4s-merger-without-stem-migration.pdf}
    \caption{
        \textbf{Predicted \bm{$f_4$} between pairs of contemporary human populations
        and ancient branches from the merger-without-stem-migration model.}
        $f_4^2(A, B; X, Y)/f_2(A, B)f_2(X, Y)$ is interpreted as the proportion of the
        amount of drift between sampled populations $A$ and $B$ that aligns with
        drift between populations $X$ and $Y$, sampled in the past
        (see Section~\ref{sec:f4}).
        Unlike the continuous-migration model, population structure in the stems
        following the divergence of Neanderthal and human ancestors results
        in differentiation among contemporary populations that aligns with drift
        between the stems. In this model, migration between stem populations
        is disallowed.
    }
    \label{fig:supp-f4s-merger-without-stem-migration}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics{figures/supp-f4s-merger-with-stem-migration.pdf}
    \caption{
        \textbf{Predicted \bm{$f_4$} between pairs of contemporary populations
        and ancient branches from the merger-with-stem-migration model.}
        $f_4^2(A, B; X, Y)/f_2(A, B)f_2(X, Y)$ is interpreted as the proportion of the
        amount of drift between sampled populations $A$ and $B$ that aligns with
        drift between populations $X$ and $Y$, sampled in the past
        (see Section~\ref{sec:f4}).
        Differentiation between present-day populations aligns with
        up to $\approx 5\%$ of the drift between stems, although some
        population pairs show even less shared drift.
    }
    \label{fig:supp-f4s-merger-with-stem-migration}
\end{figure}
